---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = file.path("man", "figures", "README-"),
  out.width = "100%"
)
```

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![License](https://img.shields.io/badge/license-MIT-blue.svg?style=flat)](https://opensource.org/licenses/MIT)
[![Release](https://img.shields.io/github/release/b-cubed-eu/simcuber.svg)](https://github.com/b-cubed-eu/simcuber/releases)
![GitHub](https://img.shields.io/github/license/b-cubed-eu/simcuber)
[![R build status](https://github.com/b-cubed-eu/simcuber/workflows/check%20package%20on%20main/badge.svg)](https://github.com/b-cubed-eu/simcuber/actions)
![GitHub code size in bytes](https://img.shields.io/github/languages/code-size/b-cubed-eu/simcuber.svg)
![GitHub repo size](https://img.shields.io/github/repo-size/b-cubed-eu/simcuber.svg)
[![R-CMD-check](https://github.com/b-cubed-eu/simcuber/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/b-cubed-eu/simcuber/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/b-cubed-eu/simcuber/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/b-cubed-eu/simcuber/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

# simcuber

The goal of **simcuber** is to provide a simulation framework for biodiversity data cubes using the R programming language. This can start from simulating multiple species distributed in a landscape over a temporal scope. In a second phase, the simulation of a variety of observation processes and effort can generate actual occurrence datasets. Based on their (simulated) spatial uncertainty, occurrences can then be designated to a grid to form a data cube.

Simulation studies offer numerous benefits due to their ability to mimic real-world scenarios in controlled and customizable environments. Ecosystems and biodiversity data are very complex and involve a multitude of interacting factors. Simulations allow researchers to model and understand the complexity of ecological systems by varying parameters such as spatial and/or temporal clustering, species prevalence, etc.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("b-cubed-eu/simcuber")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(simcuber)
```

...
